Correlation tests

### 2025-03-27 analysis/manuscript.qmd
Frit draft of discussion (limitation, furutre studies, conclusion lacking)

    % Legend
    \node [datasource, scale=0.7] at ($(analysis)+(4,0)$) {Data Sources};
    \node [process, scale=0.7] at ($(analysis)+(4,-1)$) {Processing Steps};
    \node [output, scale=0.7] at ($(analysis)+(4,-2)$) {Output};
\end{tikzpicture}
\caption{Data processing workflow for comparing hybrid open access uptake across bibliometric data sources. The workflow shows how data from different sources (Crossref, OpenAlex, JCT, Web of Science, and Scopus) is processed and matched using ROR identifiers to enable comparative analysis. TA = Transformative Agreement}
\label{fig:workflow}
\end{figure}

@@

hoaddata, developed and maintained by the author to support open access monitoring and research [@Jahn_2025], is an R data package collecting information on hybrid open access uptake from multiple openly available data sources [@hoaddata].
It combines article-level metadata from Crossref and OpenAlex with transformative agreement information from the cOAlition S Journal Checker Tool (JCT), which links journal and institutional data to agreements in the ESAC registry.

As discussed elsewhere [@Jahn_2025], hoaddata uses a unified dataset of various safeguarded JCT snapshots.
Journal data were enriched with ISSN variants linked to an ISSN-L and institution data with associated ROR-IDs representing university hospitals or institutes of large research organisations, according to OpenAlex' institution entity.
A comprehensive exclusion of fully open access journals using multiple journal lists (DOAJ, OpenAlex, Bielefeld)  was performed to identify hybrid journals.
hoaddata relies on Crossref for obtaining journal publication volume and open access status through Creative Commons licence information relative to the published version ("version of record").
Because of limited affiliation metadata in Crossref [@van_Eck_2022], hoaddata sources  affiliation metadata from OpenAlex.

@@

While hoaddata only covers articles with a DOI, Scopus and Web of Science publication indicators were calculated using their database identifier.
A subsequent comparison of DOI coverage shows that non-original articles in Web of Science often lacked a DOI.
This was particularly the case for meeting abstracts, which are notably prevalent in Health Sciences journals [@Melero_Fuentes_2025] and are not indexed by Scopus [@Donner_2017].
Open access indicators were aggregated by DOI, as Unpaywall only collects information on open access status for articles with a DOI.
A closer look at original articles with affiliation data reveals a lack of data on corresponding authors in the case of OpenAlex, the affiliation data source used by hoaddata, compared to Web of Science and Scopus.
Only about two-thirds of the articles examined provided corresponding author affiliations.
For first authors, the proportion was `r methods_overview_table_df |> filter(indicator == "First author articles") |> pull(hoad) / methods_overview_table_df |> filter(indicator == "Core articles with DOI") |> pull(hoad) * 100`%.
Therefore, only first author data for hoaddata were considered in the following analysis.

@@

In terms of article coverage, Figure \ref{fig-upset_coverage_results}B shows the total publication volume per combination in terms of DOI availability.
The largest set of hybrid journals, which includes all three data sources, also contains the largest number of articles. 
In total, these journals recorded `r upset_data |> filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE) |> pull(overlap) |> sum()` overlapping articles, represented by the blue bar. They represented `r round(upset_data |> filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE) |> pull(overlap) |> sum() / methods_overview_table_df |> filter(indicator == "Core articles with DOI") |> pull(wos) * 100)`% of original articles with DOI indexed in the Web of Science sample, and `r round(upset_data |> filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE) |> pull(overlap) |> sum() / methods_overview_table_df |> filter(indicator == "Core articles with DOI") |> pull(scp) * 100)`% in Scopus.
Another `r upset_data |> filter(Crossref == TRUE, WoS == FALSE, Scopus == TRUE) |> pull(n_cr) |> sum()` articles were exclusive to both Scopus and hoaddata. Exclusively in hoaddata were `r upset_data |> filter(Crossref == TRUE, WoS == FALSE, Scopus == FALSE) |> pull(n_cr) |> sum()` articles, and exclusively in the proprietary databases were `r upset_data |> filter(Crossref == FALSE, Scopus == TRUE) |> pull(overlap) |> sum(na.rm = TRUE)` articles.

@@

<!-- [juan study] larger proportion of hybrid, suggest journals included which might not be covered by transformative agreement. -->

@@

>>>>

    % Legend
    \node [datasource, scale=0.7] at ($(analysis)+(4,0)$) {Data Sources};
    \node [process, scale=0.7] at ($(analysis)+(4,-1)$) {Processing Steps};
    \node [output, scale=0.7] at ($(analysis)+(4,-2)$) {Output};
\end{tikzpicture}
\caption{Data processing workflow for comparing hybrid open access uptake across bibliometric data sources. The workflow shows how data from different sources (hoaddata, derived from Crossref, OpenAlex, Transformative Agreement Data dump used by the cOAlition S Journal Checker Tool (JCT), the Web of Science, and Scopus) is processed and matched using ROR IDs to enable comparative analysis. TA = Transformative Agreement.}
\label{fig:workflow}
\end{figure}

@@

hoaddata, developed and maintained by the author to support open access monitoring and research [@Jahn_2025], is an R data package that regularly collects information on hybrid open access uptake from multiple openly available data sources [@hoaddata].
It combines article-level metadata from Crossref [@Hendricks_2020] and OpenAlex [@priem2022openalex] with transformative agreement information from Transformative Agreement Data dump used by the cOAlition S Journal Checker Tool (JCT)[^tadump], which links journal and institutional data to agreements in the ESAC registry.

As discussed elsewhere [@Jahn_2025], hoaddata uses a unified dataset of various safeguarded JCT snapshots [^jct_data].
Journal data were enriched with ISSN variants linked to an ISSN-L and institution data with associated ROR-IDs representing university hospitals or institutes of large research organisations, according to OpenAlex' institution entity.
A comprehensive exclusion of fully open access journals using multiple journal lists (DOAJ, OpenAlex, Bielefeld)  was performed to identify hybrid journals.
hoaddata relies on Crossref for obtaining journal publication volume and open access status through Creative Commons licence information relative to the published version ("version of record").
Because of limited affiliation metadata in Crossref [@van_Eck_2022], hoaddata sources  affiliation metadata from OpenAlex.

@@

While hoaddata only covers articles with a DOI, Scopus and Web of Science publication indicators were calculated using their database identifier.
A subsequent comparison of DOI coverage shows that non-original articles in Web of Science often lacked a DOI.
This was particularly the case for meeting abstracts, which are notably prevalent in Health Sciences journals [@Melero_Fuentes_2025] and are not indexed by Scopus [@Donner_2017].
Open access indicators were aggregated by DOI, as Unpaywall only collects information on open access status for articles with a DOI.
A closer look at original articles with affiliation data reveals a lack of data on corresponding authors in the case of OpenAlex, the affiliation data source used by hoaddata, compared to Web of Science and Scopus.
Only about two-thirds of the articles examined provided corresponding author affiliations.
For first authors, the proportion was `r methods_overview_table_df |> filter(indicator == "First author articles") |> pull(hoad) / methods_overview_table_df |> filter(indicator == "Original articles with DOI") |> pull(hoad) * 100`%.
Therefore, only first author data for hoaddata were considered in the following analysis.

@@

In terms of article coverage, Figure \ref{fig-upset_coverage_results}B shows the total publication volume per combination in terms of DOI availability.
The largest set of hybrid journals, which includes all three data sources, also contains the largest number of articles. 
In total, these journals recorded `r upset_data |> filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE) |> pull(overlap) |> sum()` overlapping articles, represented by the blue bar. They represented `r round(upset_data |> filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE) |> pull(overlap) |> sum() / methods_overview_table_df |> filter(indicator == "Original articles with DOI") |> pull(wos) * 100)`% of original articles with DOI indexed in the Web of Science sample, and `r round(upset_data |> filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE) |> pull(overlap) |> sum() / methods_overview_table_df |> filter(indicator == "Original articles with DOI") |> pull(scp) * 100)`% in Scopus.
Another `r upset_data |> filter(Crossref == TRUE, WoS == FALSE, Scopus == TRUE) |> pull(n_cr) |> sum()` articles were exclusive to both Scopus and hoaddata. Exclusively in hoaddata were `r upset_data |> filter(Crossref == TRUE, WoS == FALSE, Scopus == FALSE) |> pull(n_cr) |> sum()` articles, and exclusively in the proprietary databases were `r upset_data |> filter(Crossref == FALSE, Scopus == TRUE) |> pull(overlap) |> sum(na.rm = TRUE)` articles.

@@

Investigating over 13,000 hybrid journals included in the cOAlition Journal Checker Tool shows a substantial increase in  open access enabled by transformative agreements between 2019 and 2023, although most articles in these journals remained paywalled during this five-year period.
While transformative agreements accounted for the majority of open access, a considerable number of open access articles are likely to have resulted from the payment of individual publication fees.
The results confirm that transformative agreements and hybrid open access continue to be concentrated among a few large commercial publishers.
They also highlight that high-income European countries in particular are using transformative agreements to make most of their article output open access, although South Africa showed similar levels of open access adoption. 
These trends were consistent across the investigated open data source hoaddata, derived from Crossref and OpenAlex, and the established proprietary bibliometric databases Scopus and Web of Science.

Comparing the data sources examined, the study results show strong correlations by country affiliation, despite differences in journal and article coverage, and in the availability of metadata on corresponding authorship and open access status. 
However, several notable discrepancies warrant discussion.
They stem not only from known limitations of the open scholarly metadata sources Crossref and OpenAlex, but also from the proprietary databases Scopus and Web of Science.

The coverage analysis reveals that hybrid journals are well indexed in all three data sources, particularly in terms of article coverage.
Differences can be found for journals targeting practitioners or local non-English language communties, with many such titles indexed exclusively in Crossref and Scopus.
Using the open index Crossref demonstrated particular strength in identifying newly established hybrid journals, a notable finding given that transformative agreements primarily target existing subscription-based journals.

The situation of hybrid journal publishing is therefore different from that of fully open access journals.
Comparing the coverage of OpenAlex, Scopus and Web of Science, @Simard_2024 indicate that only half of the fully open access journals listed in the DOAJ are also indexed in Scopus and Web of Science.
Notably, journals that charge no publication fees ("diamond journals") are absent from the selective Web of Science, which reinforces existing disparities in the indexing of underrepresented research communities and regions in selective bibliometric databases (ref).

A notable advantage of using Scopus and Web of Science to study the impact of transformative agreements is their comprehensive differentiation of journal articles by document type, as many agreements restrict funding to eligible article types. 
This resulted in slightly higher rates of open access uptake compared to hoaddata.

A similar limitation of studying open access with open scholarly data sources is the often reported lack of corresponding authorship information. 
However, indicators using first authors, which have often been used as a proxy for determining open access funding, and corresponding authors show a high level of correlation, which is not surprising given disciplinary norms in scholarly publishing. 
First authors are often considered to have carried out the main research underlying a paper, while the corresponding author is often recognised as having supervised a paper. 
It is therefore not surprising that both are strongly correlated, suggesting that first and corresponding authors share the same country affiliation.
Moreover, in most cases the first author is indeed the same as the corresponding author. As such, first authorship can be used confidentially in large-scale studies and those focusing on national consortia to assess the impact of transformative agreements.

However, affiliation data is sparser in OpenAlex than in Scopus and Web of Science, resulting in slightly more articles that could be attributed to transformative agreements. 
However, in order to establish a link, a thorough mapping of the database affiliation identifier to the ROR ID, the JCT's identifier for institutional participation in transformative agreements, is required.
In contrast, ROR IDs are the canonical organisation identifier in OpenAlex, allowing for less ambiguous matching between agreement and publication.

Comparison of scholarly databases is also valuable in identifying differences in open access identification. 
Not all publishers deposit a Creative Commons licence with Crossref, the citation authority.
A collaboration with Scopus and Web of Science helped to identify such publishers, as their underlying unpaywall data also parses licence information from websites.
However, there were significant differences between Scopus and Web of Science in terms of open access indexing, particularly with regard to the delayed open access provided by Elsevier.
In the case of Wiley, however, there were also problems with the analysis of the Unpaywall.
This suggests that hybrid open access studies should not only refer to a single source of evidence.
Instead, open access tags can be validated by the combiantion of seevral data sources, as in our case where metadata from publishers was compared with data from open access discovery services such as Unpaywall.
It is also particularly useful to include a curated list of journals under the hybrid model to avoid misclassifications based on a journal's business model [@Visser_2021].

<!-- Limitations: agreeemnts are complex, game auhtorship, invoicing not available, mapping, not feasible, requires more insitutional and publsihjer case studies involving financial data, but also improved and streamlined metadata compliance according to the evlolving stadatrd and iniatives (ESAC, Varcelona) in negotiation with publishers.

Overall, -->

<!--Journal indexing is also influenced by the open access evidence source used. 
Using the same list of hybrid journals, the results show consoderable difference in indexing, because of different approach to identify open access.
(coverage)

(document types)
( correpsonding auhtor)
(open access)
(pids)

<!-- Hybird journals are very well indexed in both proprietory and open sources. confirms the  large concentrartion of publieher there is a much a less advantage of using openalex in terms of includindg missing ones as in comparision to full opena ccess jorunals with or without APCs (also called diamond oa). Previouly reported hybrid obsvered surplus is likely due to miscoding of full open access jorunals, as they cannot been found in list of transofrmative jorunals.
However, uuing open schoalrly sources ournals with local audience  can be helpful to determine newly launched hybrid jorunals, as well as journals with local audience which is surprisingly given that transformative agreemnt are intented to shift the business modell of extisting ubscripton.based journal.

Combining different open access evidence sources

Authorship

confirm metadata gaps, in particular document types. hoewever, it is often unclear, which are incldued in transformative agreements. but metadata gaps ar enot just to be found in openalex, but also in . Lack oif ror ids to incldue this. only a workaroudn made it possible to establish a link. a manual curation is not feaible given the amoutn of transformative agreements possible.

the observed increae provide oppoirtunites for improved meatdata. negotiator have leverage, funder start using  open arrpaoches, standardisatuion activities in . These demosntrate the added value of transformative agrrements.

The increasing trend with is consistent with previous research and case studie that describe an general increase with the introduction of transformative agreements. For example, Sweden reproted

In terms of metadata coverage and quality, it shows the value of combining

that,a t least at the country level, resuts between first and correpsodnign auhtor are storngyl correlated. 
In line with empricial research, showing that morst first auhtros were also correposnding auhtor. 
This can be explained by norm of auhtorship where fir

The study deomnstrates the impact of transformative agreements on hybrid open access being consistent across biliometric data 
 [juan study] larger proportion of hybrid, suggest journals included which might not be covered by transformative agreement, oa journals not tagged as fully oa, 741268 withouht any publisher. -->

@@

[^tadump]: <https://journalcheckertool.org/transformative-agreements/>

[^jct_data]: <https://github.com/njahn82/jct_data>

### 2025-03-27 analysis/manuscript.tex
Frit draft of discussion (limitation, furutre studies, conclusion lacking)

hoaddata, developed and maintained by the author to support open access
monitoring and research (Jahn, 2025), is an R data package collecting
information on hybrid open access uptake from multiple openly available
data sources (Jahn, 2024). It combines article-level metadata from
Crossref and OpenAlex with transformative agreement information from the
cOAlition S Journal Checker Tool (JCT), which links journal and
institutional data to agreements in the ESAC registry.

As discussed elsewhere (Jahn, 2025), hoaddata uses a unified dataset of
various safeguarded JCT snapshots. Journal data were enriched with ISSN
variants linked to an ISSN-L and institution data with associated
ROR-IDs representing university hospitals or institutes of large
research organisations, according to OpenAlex' institution entity. A
comprehensive exclusion of fully open access journals using multiple
journal lists (DOAJ, OpenAlex, Bielefeld) was performed to identify
hybrid journals. hoaddata relies on Crossref for obtaining journal
publication volume and open access status through Creative Commons
licence information relative to the published version (``version of
record''). Because of limited affiliation metadata in Crossref (Eck \&
Waltman, 2022), hoaddata sources affiliation metadata from OpenAlex.

@@

While hoaddata only covers articles with a DOI, Scopus and Web of
Science publication indicators were calculated using their database
identifier. A subsequent comparison of DOI coverage shows that
non-original articles in Web of Science often lacked a DOI. This was
particularly the case for meeting abstracts, which are notably prevalent
in Health Sciences journals (Melero-Fuentes et al., 2025) and are not
indexed by Scopus (Donner, 2017). Open access indicators were aggregated
by DOI, as Unpaywall only collects information on open access status for
articles with a DOI. A closer look at original articles with affiliation
data reveals a lack of data on corresponding authors in the case of
OpenAlex, the affiliation data source used by hoaddata, compared to Web
of Science and Scopus. Only about two-thirds of the articles examined
provided corresponding author affiliations. For first authors, the
proportion was \%. Therefore, only first author data for hoaddata were
considered in the following analysis.

@@

In terms of article coverage, Figure \ref{fig-upset_coverage_results}B
shows the total publication volume per combination in terms of DOI
availability. The largest set of hybrid journals, which includes all
three data sources, also contains the largest number of articles. In
total, these journals recorded 6,289,687 overlapping articles,
represented by the blue bar. They represented \% of original articles
with DOI indexed in the Web of Science sample, and \% in Scopus. Another
657,697 articles were exclusive to both Scopus and hoaddata. Exclusively
in hoaddata were 177,110 articles, and exclusively in the proprietary
databases were 325,194 articles.

@@

@@

@@

@@

>>>>

hoaddata, developed and maintained by the author to support open access
monitoring and research (Jahn, 2025), is an R data package that
regularly collects information on hybrid open access uptake from
multiple openly available data sources (Jahn, 2024). It combines
article-level metadata from Crossref (Hendricks et al., 2020) and
OpenAlex (Priem et al., 2022) with transformative agreement information
from Transformative Agreement Data dump used by the cOAlition S Journal
Checker Tool (JCT)\footnote{\url{https://journalcheckertool.org/transformative-agreements/}},
which links journal and institutional data to agreements in the ESAC
registry.

As discussed elsewhere (Jahn, 2025), hoaddata uses a unified dataset of
various safeguarded JCT snapshots \footnote{\url{https://github.com/njahn82/jct_data}}.
Journal data were enriched with ISSN variants linked to an ISSN-L and
institution data with associated ROR-IDs representing university
hospitals or institutes of large research organisations, according to
OpenAlex' institution entity. A comprehensive exclusion of fully open
access journals using multiple journal lists (DOAJ, OpenAlex, Bielefeld)
was performed to identify hybrid journals. hoaddata relies on Crossref
for obtaining journal publication volume and open access status through
Creative Commons licence information relative to the published version
(``version of record''). Because of limited affiliation metadata in
Crossref (Eck \& Waltman, 2022), hoaddata sources affiliation metadata
from OpenAlex.

@@

While hoaddata only covers articles with a DOI, Scopus and Web of
Science publication indicators were calculated using their database
identifier. A subsequent comparison of DOI coverage shows that
non-original articles in Web of Science often lacked a DOI. This was
particularly the case for meeting abstracts, which are notably prevalent
in Health Sciences journals (Melero-Fuentes et al., 2025) and are not
indexed by Scopus (Donner, 2017). Open access indicators were aggregated
by DOI, as Unpaywall only collects information on open access status for
articles with a DOI. A closer look at original articles with affiliation
data reveals a lack of data on corresponding authors in the case of
OpenAlex, the affiliation data source used by hoaddata, compared to Web
of Science and Scopus. Only about two-thirds of the articles examined
provided corresponding author affiliations. For first authors, the
proportion was 89\%. Therefore, only first author data for hoaddata were
considered in the following analysis.

@@

In terms of article coverage, Figure \ref{fig-upset_coverage_results}B
shows the total publication volume per combination in terms of DOI
availability. The largest set of hybrid journals, which includes all
three data sources, also contains the largest number of articles. In
total, these journals recorded 6,289,687 overlapping articles,
represented by the blue bar. They represented 94\% of original articles
with DOI indexed in the Web of Science sample, and 86\% in Scopus.
Another 657,697 articles were exclusive to both Scopus and hoaddata.
Exclusively in hoaddata were 177,110 articles, and exclusively in the
proprietary databases were 325,194 articles.

@@

Investigating over 13,000 hybrid journals included in the cOAlition
Journal Checker Tool shows a substantial increase in open access enabled
by transformative agreements between 2019 and 2023, although most
articles in these journals remained paywalled during this five-year
period. While transformative agreements accounted for the majority of
open access, a considerable number of open access articles are likely to
have resulted from the payment of individual publication fees. The
results confirm that transformative agreements and hybrid open access
continue to be concentrated among a few large commercial publishers.
They also highlight that high-income European countries in particular
are using transformative agreements to make most of their article output
open access, although South Africa showed similar levels of open access
adoption. These trends were consistent across the investigated open data
source hoaddata, derived from Crossref and OpenAlex, and the established
proprietary bibliometric databases Scopus and Web of Science.

Comparing the data sources examined, the study results show strong
correlations by country affiliation, despite differences in journal and
article coverage, and in the availability of metadata on corresponding
authorship and open access status. However, several notable
discrepancies warrant discussion. They stem not only from known
limitations of the open scholarly metadata sources Crossref and
OpenAlex, but also from the proprietary databases Scopus and Web of
Science.

The coverage analysis reveals that hybrid journals are well indexed in
all three data sources, particularly in terms of article coverage.
Differences can be found for journals targeting practitioners or local
non-English language communties, with many such titles indexed
exclusively in Crossref and Scopus. Using the open index Crossref
demonstrated particular strength in identifying newly established hybrid
journals, a notable finding given that transformative agreements
primarily target existing subscription-based journals.

The situation of hybrid journal publishing is therefore different from
that of fully open access journals. Comparing the coverage of OpenAlex,
Scopus and Web of Science, Simard et al. (2024) indicate that only half
of the fully open access journals listed in the DOAJ are also indexed in
Scopus and Web of Science. Notably, journals that charge no publication
fees (``diamond journals'') are absent from the selective Web of
Science, which reinforces existing disparities in the indexing of
underrepresented research communities and regions in selective
bibliometric databases (ref).

A notable advantage of using Scopus and Web of Science to study the
impact of transformative agreements is their comprehensive
differentiation of journal articles by document type, as many agreements
restrict funding to eligible article types. This resulted in slightly
higher rates of open access uptake compared to hoaddata.

A similar limitation of studying open access with open scholarly data
sources is the often reported lack of corresponding authorship
information. However, indicators using first authors, which have often
been used as a proxy for determining open access funding, and
corresponding authors show a high level of correlation, which is not
surprising given disciplinary norms in scholarly publishing. First
authors are often considered to have carried out the main research
underlying a paper, while the corresponding author is often recognised
as having supervised a paper. It is therefore not surprising that both
are strongly correlated, suggesting that first and corresponding authors
share the same country affiliation. Moreover, in most cases the first
author is indeed the same as the corresponding author. As such, first
authorship can be used confidentially in large-scale studies and those
focusing on national consortia to assess the impact of transformative
agreements.

However, affiliation data is sparser in OpenAlex than in Scopus and Web
of Science, resulting in slightly more articles that could be attributed
to transformative agreements. However, in order to establish a link, a
thorough mapping of the database affiliation identifier to the ROR ID,
the JCT's identifier for institutional participation in transformative
agreements, is required. In contrast, ROR IDs are the canonical
organisation identifier in OpenAlex, allowing for less ambiguous
matching between agreement and publication.

Comparison of scholarly databases is also valuable in identifying
differences in open access identification. Not all publishers deposit a
Creative Commons licence with Crossref, the citation authority. A
collaboration with Scopus and Web of Science helped to identify such
publishers, as their underlying unpaywall data also parses licence
information from websites. However, there were significant differences
between Scopus and Web of Science in terms of open access indexing,
particularly with regard to the delayed open access provided by
Elsevier. In the case of Wiley, however, there were also problems with
the analysis of the Unpaywall. This suggests that hybrid open access
studies should not only refer to a single source of evidence. Instead,
open access tags can be validated by the combiantion of seevral data
sources, as in our case where metadata from publishers was compared with
data from open access discovery services such as Unpaywall. It is also
particularly useful to include a curated list of journals under the
hybrid model to avoid misclassifications based on a journal's business
model (Visser et al., 2021).

@@

\bibitem[\citeproctext]{ref-Hendricks_2020}
Hendricks, G., Tkaczyk, D., Lin, J., \& Feeney, P. (2020). Crossref: The
sustainable source of community-owned scholarly metadata.
\emph{Quantitative Science Studies}, \emph{1}(1), 414--427.
\url{https://doi.org/10.1162/qss_a_00022}

@@

\bibitem[\citeproctext]{ref-priem2022openalex}
Priem, J., Piwowar, H., \& Orr, R. (2022). \emph{OpenAlex: A fully-open
index of scholarly works, authors, venues, institutions, and concepts}.
\url{https://arxiv.org/abs/2205.01833}

@@

\bibitem[\citeproctext]{ref-Simard_2024}
Simard, M.-A., Basson, I., Hare, M., Lariviere, V., \& Mongeon, P.
(2024). \emph{The open access coverage of OpenAlex, scopus and web of
science}. \url{https://doi.org/10.48550/ARXIV.2404.01985}
